---
title: "Hacaton fanfics Harry Potter"
author: "anna kvach"
date: "1/16/2021"
output:
  html_document:
    toc: yes
    number_sections: yes
    toc_depth: 4
    theme: united
    highlight: tango
  pdf_document:
    toc: yes
    toc_depth: '4'
---

# sessionInfo

```{r}
sessionInfo()
```

# Prepare packages

## Install packages

For package installation we used function from - <https://stackoverflow.com/a/31620488>. 

It will check for missing packages and install them + it will query both - CRAN and Bioconductor repositories for missing package.


```{r}

install.packages.auto <- function(x) { 
  x <- as.character(substitute(x)) 
  if(isTRUE(x %in% .packages(all.available=TRUE))) { 
    eval(parse(text = sprintf("require(\"%s\")", x)))
  } else { 
    #update.packages(ask= FALSE) #update installed packages.
    eval(parse(text = sprintf("install.packages(\"%s\", dependencies = TRUE)", x)))
  }
  if(isTRUE(x %in% .packages(all.available=TRUE))) { 
    eval(parse(text = sprintf("require(\"%s\")", x)))
  } else {
    source("http://bioconductor.org/biocLite.R")
    #biocLite(character(), ask=FALSE) #update installed packages.
    eval(parse(text = sprintf("biocLite(\"%s\")", x)))
    eval(parse(text = sprintf("require(\"%s\")", x)))
  }
}

```

```{r}
install.packages.auto("jsonlite")
install.packages.auto("tibble")
install.packages.auto("dplyr")
install.packages.auto("stringr")
install.packages.auto("tidyr")

install.packages.auto("treemap")
install.packages.auto("ggplot2")
install.packages.auto("treemapify")
install.packages.auto("scales")
install.packages.auto("ggthemes")
```

## Library packages

```{r}
library(jsonlite)
library(tibble)
library(dplyr)
library(stringr)
library(tidyr)


library(treemap)
library(RColorBrewer)
display.brewer.all(colorblindFriendly = T)
library(ggplot2)
library(treemapify)
library(scales)
library(ggthemes)
```

## Import data

Put in file_name path to the data.

It is will be better to have empty R-environment before jsonlite::stream_in()

file_name <- '/home/anna/hacaton_2021_potter/hacaton_hp/data/FicBook_Metadata_full.json'
rd <- jsonlite::stream_in(textConnection(readLines(file_name)), verbose=F)


```{r}

file_name <- '/home/anna/hacaton_2021_potter/hacaton_hp/data/FanFics_Metadata_full.json'
rd <- jsonlite::stream_in(textConnection(readLines(file_name)), verbose=F)
```

# delete cols

```{r}
rd$ID <- NULL
rd$Authors <- NULL
rd$Series <- NULL
rd$Thanks <- NULL
rd$Author.note <- NULL
rd$Contents <- NULL
```

```{r}
colnames(rd)
```


### str flatten
```{r}
rd <- flatten(rd)

```


## as_data_frame

```{r}
rd <- as_data_frame(rd)
rd

raw_data <- rd
```

# to show "Гарри Поттер" in Characters

```{r}
rd %>% mutate(Characters = as.character(Characters)) %>% select(Characters) %>%
 filter(str_detect(Characters, "Гарри Поттер"))
```
# to unnest

```{r}
names_of_Characters <- rd %>%
 unnest(Characters) %>%
 select(name)

names_of_Characters
```

```{r}
all_ch_names <- names_of_Characters$name

length(all_ch_names)

length(unique(all_ch_names))

ch_names <- unique(all_ch_names)

head(sort(ch_names), 100)


```
```{r}
genre_data <- as.data.frame(table(all_ch_names))

sort_genre_data <- subset(genre_data, Freq > 100)

sort_genre_data
genre_data
```
```{r}
ggplot(genre_data, aes(x=Freq)) + geom_histogram(bins = 70, color="darkblue", fill="lightblue") +
  theme_minimal()+theme(legend.position="top") +
labs(title="Characters histogram plot",x = "Characters", y = "Density")
```
reorder(day, -perc)


```{r}
head(sort_genre_data$all_ch_names)

ch_sex <- c("m", "m", "m", 
            "f", "m", "m", 
            "f", "m", "m", 
            "m", "f", "m", 
            "m", "f", "m", 
            "m", "m", "f",
            "f", "m", "f",
            "m", "f", "f",
            "f", "m", "z",
            "f", "f", "m", 
            "z", "f", "f",
            "m", "m", "m", 
            "m", "m", "f",
            "m", "m", "m", 
            "m", "m", "m", 
            "m")

ch_sex <- as.factor(ch_sex)

```



```{r}
# Barplot
ggplot(sort_genre_data, aes(x = reorder(all_ch_names, Freq), y = Freq, fill=as.factor(ch_sex))) + 
  geom_bar(stat = "identity", color="white") +
  coord_flip() +
  labs(title="Characters top-100", x = "Characters", y = "Density") +
  theme_minimal()+theme(legend.position="top") + 
  scale_colour_colorblind() + labs(fill = "Sex: ")
```

```{r}
ch_names_1 <- sort_genre_data$all_ch_names

ch_rfeq_1 <- sort_genre_data$Freq

ch_sex_1  <- c("m", "m", "m", 
            "f", "m", "m", 
            "f", "m", "m", 
            "m", "f", "m", 
            "m", "f", "m", 
            "m", "m", "f",
            "f", "m", "f",
            "m", "f", "f",
            "f", "m", "z",
            "f", "f", "m", 
            "z", "f", "f",
            "m", "m", "m", 
            "m", "m", "f",
            "m", "m", "m", 
            "m", "m", "m", 
            "m")

x <- data.frame(ch_names_1, ch_rfeq_1, ch_sex_1)

write.csv(x=x, file="myFileName.csv")

```

# pairing

c("Гермиона Грейнджер", "Панси Паркинсон")

```{r}
rd %>% mutate(Pairings = as.character(Pairings)) %>% select(Pairings) 
```


# to show dates

 as.Date(df$Date, "%m/%d/%Y

```{r}
head(rd$Dates.published)
rd$
rd$Dates.published <- as.Date(rd$Dates.published, "%d.%m.%Y" )

rd$year_pub <- format(as.Date(rd$Dates.published, format="%d.%m.%Y"),"%Y")

head(rd$Dates.published)
```


# femslesh 

ggplot(dat, aes(date, fill=as.factor(hungry))) + 
      geom_bar()
      
      
chickens <-c(1, 2, 3, 3, 3, 4, 5, 4, 3, 4, 2, 2)
eggs <-c(0, 8, 10, 13, 16, 20, 25, 20, 18, 16, 10, 8)
values <-c(chickens, eggs)
      

```{r}

gg <- ggplot(data = rd, aes(x = year_pub, y = as.factor(Genre), fill=as.factor(Genre))) +
      geom_bar(stat = "identity") +
      labs(title = "Genre per year", x = "Date", y = NULL)   + theme_minimal()+theme(legend.position="top") + 
      scale_colour_colorblind() 

gg + labs(fill = "Genre: ")

```

```{r}
unique(rd$Genre)

values <- c("гет",     "джен",    "слэш",    "фемслэш")

ggplot(rd, aes(year_pub, values, fill=as.factor(Genre)))
p + geom_bar(stat = "identity")
```



chickens <-c(1, 2, 3, 3, 3, 4, 5, 4, 3, 4, 2, 2)
eggs <-c(0, 8, 10, 13, 16, 20, 25, 20, 18, 16, 10, 8)
values <-c(chickens, eggs)
      

```{r}

ggplot(data = rd, aes(x = year_pub, y = as.factor(Genre), fill=as.factor(Genre))) +
      geom_bar(stat = "identity") +
      labs(title = "Genre per date",
  #         subtitle = "femslesh",
           x = "Date", y = "Daily Precipitation")
```






























































