---
title: "Hacaton fanfics Harry Potter"
author: "anna kvach"
date: "1/16/2021"
output:
  html_document:
    toc: yes
    number_sections: yes
    toc_depth: 4
    theme: united
    highlight: tango
  pdf_document:
    toc: yes
    toc_depth: '4'
---

# sessionInfo

```{r}
sessionInfo()
```

# Prepare packages

## Install packages

For package installation we used function from - <https://stackoverflow.com/a/31620488>. 

It will check for missing packages and install them + it will query both - CRAN and Bioconductor repositories for missing package.


```{r}

install.packages.auto <- function(x) { 
  x <- as.character(substitute(x)) 
  if(isTRUE(x %in% .packages(all.available=TRUE))) { 
    eval(parse(text = sprintf("require(\"%s\")", x)))
  } else { 
    #update.packages(ask= FALSE) #update installed packages.
    eval(parse(text = sprintf("install.packages(\"%s\", dependencies = TRUE)", x)))
  }
  if(isTRUE(x %in% .packages(all.available=TRUE))) { 
    eval(parse(text = sprintf("require(\"%s\")", x)))
  } else {
    source("http://bioconductor.org/biocLite.R")
    #biocLite(character(), ask=FALSE) #update installed packages.
    eval(parse(text = sprintf("biocLite(\"%s\")", x)))
    eval(parse(text = sprintf("require(\"%s\")", x)))
  }
}

```

```{r}
install.packages.auto("jsonlite")
install.packages.auto("tibble")
install.packages.auto("dplyr")
install.packages.auto("stringr")
install.packages.auto("tidyr")

install.packages.auto("treemap")
install.packages.auto("ggplot2")
install.packages.auto("treemapify")
install.packages.auto("scales")
install.packages.auto("ggthemes")
```

## Library packages

```{r}
library(jsonlite)
library(tibble)
library(dplyr)
library(stringr)
library(tidyr)


library(treemap)
library(RColorBrewer)
display.brewer.all(colorblindFriendly = T)
library(ggplot2)
library(treemapify)
library(scales)
library(ggthemes)
```

## Import data

Put in file_name path to the data.

It is will be better to have empty R-environment before jsonlite::stream_in()

```{r}
file_name <- '/home/anna/hacaton_2021_potter/hacaton_hp/data/FicBook_Metadata_full.json'
rd <- jsonlite::stream_in(textConnection(readLines(file_name)), verbose=F)

```
# Intoduction to data

## colnames
```{r}
colnames(rd)
```

### ID
```{r}
head(rd$Dedication, 5)
```

### Title
```{r}
head(rd$Title, 5)
```

### Likes
```{r}
head(rd$Likes, 5)

summary(rd$Likes)
```

### Collections
```{r}
head(rd$Collections, 5)

summary(rd$Collections)
```

### Rewards
```{r}
head(rd$Rewards, 5)
```

```{r}
rd %>% mutate(Rewards = as.character(Rewards)) %>% select(Rewards)
```

```{r}
rewards[10,]
```



### Comments
```{r}
head(rd$Comments, 5)

summary(rd$Comments)
```

### Authors
```{r}
head(rd$Authors, 5)
```

### Genre
```{r}
head(rd$Genre, 5)

unique(rd$Genre)

```

```{r}
# Create data
genre_data <- as.data.frame(table(rd$Genre))
genre_data$Freq
# "article" "femslash" "gen" "het" "mixed" "other" "slash"

# treemap
treemap(dtf = genre_data, index = "Var1", vSize = "Freq", type = "index",                           
    palette = "Set3", # Select your color palette from the RColorBrewer presets or make your own.
    title = "My Treemap", # Customize your title
    fontsize.title = 12) # Size of the title

# Create data
genre_data_2 <- data.frame(genre = c("Art", "Oth", "Gen", "Femslash",  "Het", "Mix", "Slash"), freq = c(581,  389,  28521, 1063, 32820,  4916,    20453))

# treemap
treemap(dtf = genre_data_2, index = "genre", vSize = "freq", type = "index",                           
    palette = "Paired", # Select your color palette from the RColorBrewer presets or make your own.
    title = "My Treemap", # Customize your title
    fontsize.title = 10) # Size of the title


subgroup <- paste("subgroup" , c(1,2,3,4,1,2,1,2,3), sep="-")

# Build Dataset
group <- c(rep("No relationships", 3), "Femslash", rep("With relationships", 3))
subgroup <- c("Art", "Oth", "Gen", "Fem",  "Het", "Mix", "Slash")
value <- c(581,  389,  28521, 1063, 32820, 4916, 20453)
data <- data.frame(group, subgroup, value)
 

# treemap
treemap(data, 
        index=c("group","subgroup"),
        vSize="value",
        type="index",
          
        title = "Genre", # Customize your title
        fontsize.title = 15) # Size of the title) 

```

```{r}
# Build Dataset
group <- c(rep("No relationships", 3), "Femslash", rep("With relationships", 3))
subgroup <- c("Art", "Oth", "Gen", "Fem",  "Het", "Mix", "Slash")
value <- c(581,  389,  28521, 1063, 32820, 4916, 20453)
data <- data.frame(group, subgroup, value)
data$pct <- data$value / sum(data$value) 
label_percent()(data$pct) # "Art 0.65%", "Oth 0.44%", "Gen 32.14%", "Fem 1.20%",  "Het 36.98%", "Mix 5.54%", "Slash 23.05%"
 

# treemap
ggplot(data,
       aes(area = value, 
           fill = group, 
           label = subgroup,
           subgroup = subgroup)) +

  geom_treemap() +
  geom_treemap_text() +
  labs(title = "Genre") + 
  scale_colour_colorblind()
```


### Authors
```{r}
head(rd$Authors, 5)
```

### Fandom
```{r}
head(rd$Fandom, 5)
```

### Pairings
```{r}
head(rd$Pairings, 5)
```

### Characters
```{r}
head(rd$Characters, 5)
```

```{r}
 rd %>% mutate(Characters = as.character(Characters)) %>% select(Characters)

```

```{r}
characters
```

character(0)

c("Артур Уизли", "Люциус Малфой")

Секрет

Гермиона Грейнджер





### Rating
```{r}
head(rd$Rating, 5)
```

### Size
```{r}
head(rd$Size, 5)
```
### Status
```{r}
head(rd$Status, 5)
```

### Tags
```{r}
head(rd$Tags, 5)
```

### Description
```{r}
head(rd$Description, 5)
```

### Dedication
```{r}
head(rd$Dedication, 5)
```

### Publish.permissions
```{r}
head(rd$Publish.permissions, 5)
```

### Author.note
```{r}
head(rd$Author.note, 5)
```

### Contents
```{r}
head(rd$Contents, 5)
```

============================
============================

### str flatten
```{r}
rd <- flatten(rd)
str(rd)
```










