---
title: "Hacaton fanfics Harry Potter"
author: "anna kvach"
date: "1/16/2021"
output:
  html_document:
    toc: yes
    number_sections: yes
    toc_depth: 4
    theme: united
    highlight: tango
  pdf_document:
    toc: yes
    toc_depth: '4'
---

# sessionInfo

```{r}
sessionInfo()
```

# Prepare packages

## Install packages

For package installation we used function from - <https://stackoverflow.com/a/31620488>. 

It will check for missing packages and install them + it will query both - CRAN and Bioconductor repositories for missing package.


```{r}

install.packages.auto <- function(x) { 
  x <- as.character(substitute(x)) 
  if(isTRUE(x %in% .packages(all.available=TRUE))) { 
    eval(parse(text = sprintf("require(\"%s\")", x)))
  } else { 
    #update.packages(ask= FALSE) #update installed packages.
    eval(parse(text = sprintf("install.packages(\"%s\", dependencies = TRUE)", x)))
  }
  if(isTRUE(x %in% .packages(all.available=TRUE))) { 
    eval(parse(text = sprintf("require(\"%s\")", x)))
  } else {
    source("http://bioconductor.org/biocLite.R")
    #biocLite(character(), ask=FALSE) #update installed packages.
    eval(parse(text = sprintf("biocLite(\"%s\")", x)))
    eval(parse(text = sprintf("require(\"%s\")", x)))
  }
}

```

```{r}
install.packages.auto("jsonlite")
install.packages.auto("tibble")
install.packages.auto("dplyr")
install.packages.auto("stringr")
install.packages.auto("tidyr")

install.packages.auto("treemap")
install.packages.auto("ggplot2")
install.packages.auto("treemapify")
install.packages.auto("scales")
install.packages.auto("ggthemes")
```

## Library packages

```{r}
library(jsonlite)
library(tibble)
library(dplyr)
library(stringr)
library(tidyr)


library(treemap)
library(RColorBrewer)
display.brewer.all(colorblindFriendly = T)
library(ggplot2)
library(treemapify)
library(scales)
library(ggthemes)
```

## Import data

Put in file_name path to the data.

It is will be better to have empty R-environment before jsonlite::stream_in()

file_name <- '/home/anna/hacaton_2021_potter/hacaton_hp/data/FicBook_Metadata_full.json'
rd <- jsonlite::stream_in(textConnection(readLines(file_name)), verbose=F)


```{r}

file_name <- '/home/anna/hacaton_2021_potter/hacaton_hp/data/FanFics_Metadata_full.json'
rd <- jsonlite::stream_in(textConnection(readLines(file_name)), verbose=F)
```

# delete cols

```{r}
rd$ID <- NULL
rd$Authors <- NULL
rd$Series <- NULL
rd$Thanks <- NULL
rd$Author.note <- NULL
rd$Contents <- NULL
```

```{r}
colnames(rd)
```


### str flatten
```{r}
rd <- flatten(rd)
str(rd)
```


## as_data_frame

```{r}
rd <- as_data_frame(rd)
rd
```

# to show "Гарри Поттер" in Characters

```{r}
rd %>% mutate(Characters = as.character(Characters)) %>% select(Characters) %>%
 filter(str_detect(Characters, "Гарри Поттер"))
```
# to unnest

```{r}
names_of_Characters <- rd %>%
 unnest(Characters) %>%
 select(name)

names_of_Characters
```

```{r}
all_ch_names <- names_of_Characters$name

length(all_ch_names)

length(unique(all_ch_names))

ch_names <- unique(all_ch_names)

head(sort(ch_names), 100)


```
```{r}
genre_data <- as.data.frame(table(all_ch_names))

sort_genre_data <- subset(genre_data, Freq > 100)

sort_genre_data
genre_data
```
```{r}
ggplot(genre_data, aes(x=Freq)) + geom_histogram(bins = 70, color="darkblue", fill="lightblue") +
  theme_minimal()+theme(legend.position="top") +
labs(title="Characters histogram plot",x = "Characters", y = "Density")
```
reorder(day, -perc)

```{r}
# Barplot
ggplot(sort_genre_data, aes(x = reorder(all_ch_names, -Freq), y = Freq)) + 
  geom_bar(stat = "identity", color="darkblue", fill="lightblue") +
  coord_flip() +
  labs(title="Characters top 100", x = "Characters", y = "Density") +
  theme_minimal()+theme(legend.position="top") 
```

# to show dates

```{r}
head(rd$Dates.published)
```

# pairing

c("Гермиона Грейнджер", "Панси Паркинсон")

```{r}
rd %>% mutate(Pairings = as.character(Pairings)) %>% select(Pairings) 
```



























































