---
title: "json_analise"
author: "anna kvach"
date: "1/16/2021"
output:
  pdf_document: default
  html_document: default
---

<https://blog.exploratory.io/working-with-json-data-in-very-simple-way-ad7ebcc0bb89> as manual 

------------------------------------

# Prepare packages

## Install packages

For package installation we used function from - <https://stackoverflow.com/a/31620488>. 

It will check for missing packages and install them + it will query both - CRAN and Bioconductor repositories for missing package.


```{r}

install.packages.auto <- function(x) { 
  x <- as.character(substitute(x)) 
  if(isTRUE(x %in% .packages(all.available=TRUE))) { 
    eval(parse(text = sprintf("require(\"%s\")", x)))
  } else { 
    #update.packages(ask= FALSE) #update installed packages.
    eval(parse(text = sprintf("install.packages(\"%s\", dependencies = TRUE)", x)))
  }
  if(isTRUE(x %in% .packages(all.available=TRUE))) { 
    eval(parse(text = sprintf("require(\"%s\")", x)))
  } else {
    source("http://bioconductor.org/biocLite.R")
    #biocLite(character(), ask=FALSE) #update installed packages.
    eval(parse(text = sprintf("biocLite(\"%s\")", x)))
    eval(parse(text = sprintf("require(\"%s\")", x)))
  }
}

```

```{r}
install.packages.auto("jsonlite")
install.packages.auto("tibble")
install.packages.auto("dplyr")
install.packages.auto("stringr")
install.packages.auto("tidyr")
```

## Library packages

```{r}
library(jsonlite)
library(tibble)
library(dplyr)
library(stringr)
library(tidyr)
```

## Import data

```{r}
yelp <- stream_in(file("/home/anna/hacaton_2021_potter/hacaton_hp/test_data/yelp_academic_dataset_business.json"))
```

### raw_data

#### str

```{r}
str(yelp)
```


#### view raw_data

```{r}
yelp
```

## flatten

Number of columns will increase. From hierarchia to wide format

### str flatten
```{r}
yelp_flat <- flatten(yelp)
str(yelp_flat)
```


### view flatten

```{r}
yelp_flat
```



## as_data_frame

```{r}
yelp_tbl <- as_data_frame(yelp_flat)
yelp_tbl
```
# to show data in list

```{r}
yelp_tbl %>% mutate(categories = as.character(categories)) %>% select(categories)
```


# remove cols srats with

```{r}
yelp_tbl %>% 
 select(-starts_with("hours"), -starts_with("attribute"))
```

# to choose _Mini Golf_ from _categories_

```{r}
yelp_tbl %>% select(-starts_with("hours"), -starts_with("attribute")) %>%
 filter(str_detect(categories, "Mini Golf"))
```

## to test 

```{r}
yelp_tbl %>% select(-starts_with("hours"), -starts_with("attribute")) %>%
 filter(str_detect(categories, "Mini Golf")) %>%
 mutate(categories = as.character(categories)) %>% select(categories)
```


# to unnest

```{r}
yelp_tbl %>% select(-starts_with("hours"), -starts_with("attribute")) %>%
 filter(str_detect(categories, "Mini Golf")) %>%
 unnest(categories) %>%
 select(name, categories)
```


# to count

```{r}
yelp_tbl %>% select(-starts_with("hours"), -starts_with("attribute")) %>%
 filter(str_detect(categories, "Mini Golf")) %>%
 unnest(categories) %>%
 select(name, categories) %>%
 count(categories)
```


# to arrange

```{r}
yelp_tbl %>% select(-starts_with("hours"), -starts_with("attribute")) %>%
 filter(str_detect(categories, "Mini Golf")) %>%
 unnest(categories) %>%
 select(name, categories) %>%
 count(categories) %>%
 arrange(desc(n))
```








